---
title: "Figure layer all"
author: "Dimitri Fichou"
date: "December 1, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,cache = F,dev="png",fig.width=3.33,out.width = "1000px",fig.path = "../figures/")
library(DLC)
```




\pagebreak


#### Figure 3.


```{r Layer_Fig 3,fig.height=3.33,dpi=300,results="AsIs"}
data = f.read.image(paste0("../data/plate_",c(27,35,66,68),".jpg"),height=992,ls.format = T)
data[[3]] = data[[3]][1:782,,]
data[[4]] = data[[4]][1:782,,] 

par(xaxt="n",yaxt="n",mar=c(0,0,0,0),xaxs="i",yaxs="i",mfrow=c(2,2))
for(i in seq(length(data))){
  raster(data[[i]][,1:992,],bty="o",interpolate = T)
  text(0,dim(data[[i]])[1]*0.87,labels=c("A","B","C","D")[i],pos=4,cex=2,col="white")
}
```



\pagebreak

#### Figure 4. Effect of the development direction. A: developed perpendicular to the printing path direction, 5 µL of the diluted mixture, B: developed in the direction of the printing path, 1 µL of the diluted mixture per track.

1.77/18*1000 = 98 words equivalant

```{r Layer_Fig_4,fig.height=1.77,dpi=300}
data = f.read.image(paste0("../data/plate_",c(69,73),"_developed.jpg"),height=992,ls.format = T)

par(xaxt="n",yaxt="n",mar=c(0,0,0,0),xaxs="i",yaxs="i") 
par(mfrow=c(1,2))

for(i in seq(length(data))){
  raster(data[[i]][700:1,,],interpolate = T)
  text(x=0,y=620,labels=c("A","B")[i],cex=1.5,pos=4)
}
```

\pagebreak

#### Figure 5. Semi quantitative analysis with a plate developed in the direction of the printing path. A: chromatograms, B: video densitograms extracted between the dashed lines, C: densitograms at 550 nm.

8/18*1000 = 444 words equivalant


```{r Layer_Fig_5,fig.height=8,dpi=300}
load("../data/Fig76_rtlc.RData")
VD = 1-data$chrom[,60:700,] 
data = read.table("../data/plate-76-raw-densito.txt",sep = ";",header = T)

mat = cbind(c(rep(1,6),2:9,rep(10,8)))
layout(mat)
par(mar=c(0.5,3.5,0,0.5),mgp=c(2,0.5,0),oma=c(4,0,3,0),xaxs="i",yaxs="i")
im = f.read.image("../data/plate_76_developed.jpg",992) #%>% aperm(c(2,1,3))
im = im[700:60,900:100,]
im = im%>% aperm(c(2,1,3))
im = im[,dim(im)[2]:1,]
im = im[dim(im)[1]:1,,]
raster(im,xaxt="n",yaxt="n") 

# abline(h=seq(0,800,by=10),col="red")
# abline(h=seq(0,800,by=50),col="black")
index=c(740,640,540,440,340,240,140,40) + 20
marge = 30
for(i in index){abline(h=c(index-marge,index+marge),lty=2)}
# abline(h=index)

axis(side = 2,at = index,labels = rev(c("0.5","1","2","5","0.5","1","2","5")),tick = F,cex.lab=1.5)
# axis(1,at=seq(from = 0,to = 700-60,length.out = 11),labels = seq(from = 0,to = 100,by = 10),hadj = 0.7)
# mtext(expression(italic(hR) [F]), side=1,line = 2,cex=1)
mtext(expression(paste("Applied volume (", mu, "L)")), side=2,line = 1.5,cex=1)

mtext("A", side = 3, line = 1, outer = FALSE, at = c(-70),
      adj = NA, padj = 1.2, cex = 1.5, col =NA, font = NA)


par(mar=c(0.2,3.5,0.2,0.5),xaxs="i",yaxs="r")

index = dim(im)[1] - index

im = im[dim(im)[1]:1,,]

truc = c()
truc = c(truc,expression(paste("5 ",mu,"L")))
truc = c(truc,expression(paste("2 ",mu,"L")))
truc = c(truc,expression(paste("1 ",mu,"L")))
truc = c(truc,expression(paste("0.5 ",mu,"L")))
truc = c(truc,expression(paste("5 ",mu,"L")))
truc = c(truc,expression(paste("2 ",mu,"L")))
truc = c(truc,expression(paste("1 ",mu,"L")))
truc = c(truc,expression(paste("0.5 ",mu,"L")))


ylim = c(0.4,0.85)
for(i in 1:8){
  plot(VD[i,,1],type="l",ylim=ylim ,col=c("red","green","blue")[1],xaxt="n",yaxt="n",xlab="",ylab="",cex.lab=0.6,cex.axis=0.8,cex=1)
  par(new=T)
  plot(VD[i,,2],type="l",ylim=ylim ,col=c("red","green","blue")[2],xaxt="n",mgp=c(2,1,0),xlab="",ylab="",bty="n",yaxt="n",cex.lab=0.6,cex.axis=0.7)
  par(new=T)
  plot(VD[i,,3],type="l",ylim=ylim ,col=c("red","green","blue")[3],xaxt="n",mgp=c(2,1,0),xlab="",ylab="",bty="n",yaxt="n",cex.lab=0.6,cex.axis=0.7)
  if(i == 4){
    mtext("Intensity (AU)           ", side=2,line = 2,cex=1)
  }
  axis(side = 2,at = c(0.45,0.8),labels=c("0 ","1 "),las=2,hadj = 1.2)
  if(i == 1){
    mtext("B", side = 3, line = 1, outer = FALSE, at = c(-70),
      adj = NA, padj = 1.2, cex = 1.5, col =NA, font = NA)
  }
  text(x=dim(VD)[2],y=mean(ylim),pos=2,labels=truc[i])
  par(new=F)
}
# axis(1,at=seq(from = 0,to = 700-60,length.out = 11),labels = seq(from = 0,to = 1,by = 0.1),hadj = 0.7)
mtext(expression(italic(hR) [F]), side=1,line = 2,cex=1)
axis(1,at=seq(from = 1,to = 700-60,length.out = 11),labels = seq(from = 0,to = 100,by = 10),hadj = 0.7)

mtext("C", side = 1, line = 1, outer = FALSE, at = c(-70),
      adj = NA, padj = 2, cex = 1.5, col =NA, font = NA)

par(new=F,xaxs="r")
# data = data[,c(1,9:2)]
library(scatterplot3d)
for(i in 2:9){
  if(i != 2){
    scatterplot3d(y = rep(i-1, nrow(data)),x = data[,1]*100,z=data[,i],
                  ylim=c(0,8),xlim=c(0,100),zlim = c(0,max(data[,2:9])),
                type="l",color=RColorBrewer::brewer.pal(8,"Dark2")[i-1],scale.y = 1,y.margin.add = 0.2,
                angle = 50,mar = c(3,4,2.5,0),lab = c(6,9,1),
                lty.axis = 1,lab.z = 3,
                xlab = "" , ylab = "",zlab = "",
                grid = F,box = F,tick.marks=F,label.tick.marks = F)
  }else{
    scatterplot3d(y = rep(i-1, nrow(data)),x = data[,1]*100,z=data[,i],
                  ylim=c(0,8),xlim=c(0,100),zlim = c(0,max(data[,2:9])),
                type="l",color=RColorBrewer::brewer.pal(8,"Dark2")[i-1],scale.y = 1,y.margin.add = 0.2,
                lty.axis = 3,lty.hplot = 3,
                cex.lab = 1,lty.hide = 2,angle = 50,mar = c(3,4,2.5,0),
                lab=c(6,9,1),lab.z = 3,xlab = expression(italic(hR) [F]) ,
                ylab = "",zlab = "Intensity (AU)",
                y.ticklabs = c("",  "0.5","1","2","5","0.5","1","2","5"),
                z.ticklabs = c("0","200","","600")
                )
  }
  par(new=T)
}


# text(x=8,y=1.3,labels=expression(paste("Applied volume (", mu, "L)")),srt=45,cex=1.5)

# text(x = c(2,2.4,2.8,3.2,3.6,4),y=)
par(new = T)
par(mar=rep(0,4))
plot(1,1,type="n",bty="n",xaxt="n",yaxt="n",xlab="",ylab="n")
text(x=1.3,y=0.8,labels=expression(paste("Applied volume (", mu, "L)")),srt=43,cex=1.4)
# text(y = c(1.1,0.9,1.3,1.5,1.5,1.7),x=c(1.5,1.7,1.7,1.7,1.5,1.7))#,labels=c("Dimethyl Yellow", "Oracet Red G", "Solvent Blue 35", "Sudan Red G", "Solvent Blue 22", "Oracet Violet 2R")
```

\pagebreak

#### Figure 6.


```{r Layer_Fig_6,fig.height=4.1,dpi=300}
layout(rbind(c(1,1,1,2)))
par(xaxs="i",yaxs="i",mgp=c(2,1,0))
data = f.read.image("../data/plate_87_developed_T.jpg",height=992) %>% EBImage::rotate(-0.5)
data = data[992 - 700:50,105:545,]
x = 246 
ecart = 4
# data = data[992:1,,]
# x=570+340
par(mar=c(5,3.5,0.5,0.1))
    
raster(data,xaxt="n",yaxt="n",interpolate = T)
axis(2,at=seq(from = 50,to = 600,by = (600-50)/10),labels = seq(from = 0,to = 100,by = 10),las=2,hadj = 0.7)
axis(1,at=seq(from = 1,to = dim(data)[2]*0.92,by=20),labels = seq(from = 0,to = round(dim(data)[2]*0.9/10),by = 2),hadj = 0.7)
mtext(expression(italic(hR) [F]), side=2,line = 2,cex=0.7)
mtext("Dimension (mm)", side=1,line = 2,cex=0.7)
symbols(x=x,y=dim(data)[1]/2,rectangles=rbind(c(2*ecart+4,dim(data)[1])),add=T,inches=F,lty=2)
# symbols(x=20,y=dim(data)[1]*0.96,rectangles=rbind(c(30,dim(data)[1]*0.06)),add=T,inches=F,bg = "white",fg = "white")


data = EBImage::medianFilter(data,5)

par(xaxs="r")

text(x = 0, y = dim(data)[1]*0.95,labels = "A",cex = 2,pos=4)
# xlim=c(0.15,0.37)
data.a = apply(data[dim(data)[1]:1,(x-ecart):(x+ecart),1],1,mean)
data.b = apply(data[dim(data)[1]:1,(x-ecart):(x+ecart),2],1,mean)
data.c = apply(data[dim(data)[1]:1,(x-ecart):(x+ecart),3],1,mean)
xlim=c(min(c(data.a,data.b,data.c)),max(c(data.a,data.b,data.c)))
par(mar=c(5,0.5,0.5,1))
plot(x=data.a,y=seq(dim(data)[1]),type="l",xlim=xlim,col=c("red","green","blue")[1],ylab="",yaxt="n",mgp=c(2.5,1,0),xlab="",ylim=)
par(new=T)
plot(x=data.b,y=seq(dim(data)[1]),type="l",xlim=xlim,col=c("red","green","blue")[2],ylab="",yaxt="n",mgp=c(2.5,1,0),xlab="",bty="n",xaxt="n")
par(new=T)
plot(x=data.c,y=seq(dim(data)[1]),type="l",xlim=xlim,col=c("red","green","blue")[3],ylab="",yaxt="n",mgp=c(2.5,1,0),xlab="",bty="n",xaxt="n")
par(new=T)
mtext("Intensity (AU)", side=1,line = 2,cex=0.7)
text(x = xlim[1], y = dim(data)[1]*0.95,labels = "B",cex = 2,pos=4)
par(new=F)
```




\pagebreak

#### Figure 7.


```{r Layer_Fig_7,fig.height=3.5,dpi=300}
layout(rbind(c(1,1,1,3,2,2)))
par(xaxs="i",yaxs="i",mgp=c(2,1,0),bg="white")
data = f.read.image("../data/plate_110_developed_T.jpg",height=992)
data= data[992-(700:70),110:410,] 
x = 245
ecart = 30
# data = data[992:1,,]
# x=570+340
par(mar=c(2.5,3,0.5,0.5))

ylim = c(1,300)
    
raster(data,xaxt="n",yaxt="n",ylim=ylim,interpolate = T)
axis(2,at=seq(from = 20,to = 600,by = (600-50)/10),labels = seq(from = 0,to = 100,by = 10),las=2,hadj = 0.7)
axis(1,at=c(45,145,245),labels = c(0.5,1,2),padj = -0.7,tick = F)
mtext(expression(italic(hR) [F]), side=2,line = 1.5,cex=0.7)
mtext(expression(paste("Applied volume ( ", mu, "L )")), side=1,line = 1.5,cex=0.7)
symbols(x=x,y=dim(data)[1]/2,rectangles=rbind(c(2*ecart+4,dim(data)[1])),add=T,inches=F,lty=2)
# symbols(x=20,y=dim(data)[1]*0.96,rectangles=rbind(c(30,dim(data)[1]*0.06)),add=T,inches=F,bg = "white",fg = "white")
text(y=0.95*ylim[2],x=0,pos=4,cex=2,"A")

data = EBImage::medianFilter(data,3)

par(xaxs="r")

# xlim=c(0.15,0.37)
data.a = apply(data[dim(data)[1]:1,(x-ecart):(x+ecart),1],1,mean)
data.b = apply(data[dim(data)[1]:1,(x-ecart):(x+ecart),2],1,mean)
data.c = apply(data[dim(data)[1]:1,(x-ecart):(x+ecart),3],1,mean)
xlim=c(min(c(data.a,data.b,data.c)),max(c(data.a,data.b,data.c)))
par(mar=c(2.5,0.5,0.5,0.5))
plot(x=data.a,y=seq(dim(data)[1]),type="l",xlim=xlim,col=c("red","green","blue")[1],ylab="",yaxt="n",mgp=c(2.5,1,0),xlab="",xaxt="n",ylim=ylim)
par(new=T)
plot(x=data.b,y=seq(dim(data)[1]),type="l",xlim=xlim,col=c("red","green","blue")[2],ylab="",yaxt="n",mgp=c(2.5,1,0),xlab="",bty="n",xaxt="n",ylim=ylim)
par(new=T)
plot(x=data.c,y=seq(dim(data)[1]),type="l",xlim=xlim,col=c("red","green","blue")[3],ylab="",yaxt="n",mgp=c(2.5,1,0),xlab="",bty="n",xaxt="n",ylim=ylim)
par(new=T)
axis(1,at=round(seq(xlim[1],xlim[2],by=0.1),1),padj = -0.7,tick = T)
mtext("Intensity (AU)", side=1,line = 1.5,cex=0.7)
text(y=0.95*ylim[2],x=xlim[1],pos=4,cex=2,"C")
par(new=F)

data = f.read.image(source = "../data/Screenshot HPTLC plate.png",301)
raster(data[150:285,10:70,],xaxt="n",yaxt="n",interpolate = T)
text(y=-0.95*(150-285),x=0,pos=4,cex=2,"B")
```


